Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-15 Article/ici_submm_cloudcorr.tex
added table for QRNN-mwi results, other minor changes

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}

@@

\subsection{MicroWave Imager}
%
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.

@@

The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single
across-track scanning microwave radiometer. The main objective of AWS will be
to improve representation of Artic and sub-Arctic weather in NWP models and
improve the global weather forecasts. AWS will will have channels receiving
frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
detailed description of the AWS channels see \citet{eriksson2020study}, while a
brief summary of AWS channels relevant to this study are provided in
Table~\ref{tab:specifications_AWS}.

@@

\subsection{Produced dataset}
%
Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI and MWI frequency. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land. It is also assumed that all simulations of ICI and MWI are remapped to a common foorprint.

For AWS, 24 monochromatic frequencies were simulated so that each channel could be represented with sufficient accuracy. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 130\,000 cases based on randomly selected CloudSat orbits were simulated.

\begin{table*}[t]
	\caption{Summary of the different QRNN models used in the study.}
	\label{tab:QRNN_models}
	\begin{tabular}{lllll}
		\tophline
		QRNN model & Sensor & Target & Input 183\,GHz channel &Other training inputs \\
		\middlehline
		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{2-5}
					&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
		\cline{2-5}
					& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
					&		& AWS-34/		 &	AWS-34/		   & \\
					&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
		\cline{1-5}
		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{1-5}
		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
				 &			& MWI-16/		 &  MWI-16, & \\
				 &			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
	\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table*}

\subsection{Training data}
%
The QRNN models presented in this study are trained with simulated brightness temperature data to predict the noise-free clear-sky values for 183\,GHz channels. No other data was included in the training process, but the training set varied according to the QRNN-model (described further). Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set. The rest were used for testing. For AWS a slightly smaller database was selected. Out of 130\,000 simulations, 100\,000 were used for training while the rest formed the testing set.

@@

\section{Results}
\subsection{QRNN network structure}
%
A high performing QRNN model requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. We use quantile loss and CRPS for evaluation of the model performance.

For the structural parameters, the usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. In this study, all possible hyper-parameters were not tested. We investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The others were chosen empirically.

@@

\subsection{ICI}
\subsubsection{Example results}
%
QRNN predictions are estimates of the posterior distribution over different quantiles. For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The quantiles are interpreted as probabilitic predictions and can be used to construct a probability distribution of the predictions. This is in sharp contrast to correction approaches which give out only point estimates. As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases. These results are from QRNN-single for channel I2V. The three cases shown in the figure have almost a similar median value but very different spread. The spread of the distributions can also be expressed as the prediction interval. If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval. It is gives the range where the prediction could be located and its length is a measure of the reliability. Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability. While the other two cases have longer intervals implying higher fluctuations, or low reliability.

@@

\subsubsection{Error of best estimate}
%
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure*}
%f 
\begin{figure*}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure*}

%t
\begin{table*}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V. Results from both QRNN-simple and QRNN-all are shown. The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:error_statistics_ici}
%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-single} & \multicolumn{3}{c}{QRNN-all}\\
		\cline{3-10}
%		\hline
		&&   Clear-sky &   All-sky &  Filtered & Predicted & Predicted &   Filtered & Predicted & Predicted \\
		&&&&							(5\,K) &(All)& (5\,K) & (5\,K)&(All)& (5\,K)\\
		\middlehline
%		\multicolumn{7}{c}{Channel - I1V}\\

Channel I1V& bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
			&mae      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
			&std      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
			&skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
\middlehline
Channel I2V & bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
			&mae      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
			&std      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
			&skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
\middlehline	
Channel I3V & bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
			&mae      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
			&std      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
			&skewness & -0.00 & -13.41 & -0.86 & -1.75 & -0.11 & -0.93 & -1.53 & -0.14 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

\begin{table*}[t]
	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included. The fraction of cases forming the dataset are included in the parenthesis}
	\label{tab:error_statistics_ici_high_cloud_impact}
	%	\tabcolsep=0.11cm
	\begin{tabular}{lrr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{I1V}& \multicolumn{2}{c|}{I2V} & \multicolumn{2}{c}{I3V}\\
		\cline{2-7}
		&QRNN-single& QRNN-all & QRNN-single & QRNN-all  & QRNN-single & QRNN-all\\
		\middlehline
				    bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
					mae      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
					std      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
	\caption{A comparison of the  average error bias when pure-filtering approach is applied with different thresholds (red curves). The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).  }
	\label{fig:filtering_thresholds}	
\end{figure} 
To assess the accuracy of QRNN predictions, a point estimate of the posterior distribution is required. Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted clear-sky value.

The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig.~\ref{fig:PDF_predictions}. The distributions of corresponding clear-sky simulations are also plotted as reference. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails. The degree of mismatch is highest for I1V, which incidently also has the largest spread of brightness temperatures in the clear-sky conditions. For all three channels, the colder brightness temperatures are under-estimated by QRNN, while a tendency to over-estimate the warmer brightness temperatures is seen for I1V and I2V.

For a quantitative evaluation of QRNN accuracy, the prediction errors are calculated as the deviation of the best estimate to its corresponding noise-free clear-sky values. We calculate the mean bias, mean absolute error and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments.

Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels from QRNN-single. The distribution of noise is also plotted for reference. Without any cloud impact, the error distributions should follow a Gaussian distribution, and the skewness should be close to zero. However the presence of clouds leads to a brightness temperature reduction, and introduces a high negative bias among the deviations. Among the three channels, I1V has the highest cloud impact, while I3V has the least. After correction of the cloud impact, the resulting error distributions are  symmetric with a sharper peak albeit with a large spread. The large spread is due to cases which end up with partial cloud correction and also due to cases where the predicted values are warmer than the simulations. For all three channels, quite similar behaviour is observed, though I1V has the highest number of cases with residual cloud impact. We assume that such cases are associated with high cloud impact. To validate our assumption, we implemented a pure-filtering approach. In the filtered subset, we removed all cases with QRNN cloud correction greater than 5\,K, and did not correct the remaining cases. This can be considered as a pure-filtering approach. The results from this subset are also displayed in the figure (red curve). For all three channels, the right side follows measurement noise, as expected, but the left side has substantial cases with small cloud impact which pass through the filter. However, since the spread of filtered dataset is smaller than the corrected one, it confirms our assumption that most of the partially corrected cases have high cloud impact. On the other hand, if all the predicted cases with correction less than 5\,K (Predicted (5\,K) in the figure) are considered, the resulting error distributions are quite close to the measurement noise, except for I1V, where few cases with residual cloud impact can still be seen.

@@

Similar results are seen for channel I2V, though a better performance of QRNN is observed. In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction. The mean absolute error also reduces from 1.52\,K to 0.52\,K. Removing cases with correction greater than 5\,K from the corrected dataset removes only 3.7\% of the data but reduces the absolute error to 0.46\,K and the bias to 0\,K. The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise. The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper.

>>>>

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
				& [GHz]			& [MHz]			& [K]			&\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3000			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3000			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & \phantom{0}500			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & \phantom{0}500 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
				& [GHz]			& [MHz]			& [K]			&\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2000 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1500			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1500			& 1.2 		& V\\
		MWI-17&	183.31$\pm$3.40    & 1500			& 1.2 		& V\\
		MWI-18&	183.31$\pm$2.00    & 1500			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}

@@

\subsection{MicroWave Imager}
%
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. A brief summary of the MWI 183\,GHz channels is provided in Table~\ref{tab:ICI_MWI_channels}.

@@

The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single
across-track scanning microwave radiometer. It is planned as a small but cost-effective platform, which can supplement the information from other polar orbiting satellites. The main objective of AWS will be to improve representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts. AWS will will have channels receiving frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a detailed description of the AWS channels see \citet{eriksson2020study}, while a brief summary of AWS channels relevant to this study are provided in
Table~\ref{tab:specifications_AWS}. The first prototype mission is expected to be delivered around 2023.

@@

\subsection{Produced dataset}
%
Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 220\,000 cases for each ICI and MWI frequency. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land. It is also assumed that all simulations of ICI and MWI are remapped to a common foorprint.

For AWS, 7 monochromatic frequencies were simulated each for 183\,GHz, 325\,GHz-upper amd 325\,GHz-lower, so that the channel brightness temperature for each could be represented with sufficient accuracy. The monochromatic frequencies were interpolated to a finer grid to get the channel temperatures. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 130\,000 cases based on randomly selected CloudSat orbits were simulated.

\begin{table*}[t]
	\caption{Summary of the different QRNN models used in the study.}
	\label{tab:QRNN_models}
	\begin{tabular}{lllll}
		\tophline
		QRNN model & Sensor & Target & Input 183\,GHz channel(s) &Other training inputs \\
		\middlehline
		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{2-5}
					&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
		\cline{2-5}
					& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
					&		& AWS-34/		 &	AWS-34/		   & \\
					&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
		\cline{1-5}
		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{1-5}
		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
				 &			& MWI-16/		 &  MWI-16, & \\
				 &			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
	\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table*}

\subsection{Training data}
%
The QRNN models presented in this study are trained with simulated brightness temperature data to predict the NFSC values for 183\,GHz channels. No other data was included in the training process, but the training set varied according to the QRNN-model (described further). Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set. The rest were used for testing. For AWS a slightly smaller database was selected. We had 130\,000 available simulations and all were used for training. A testing dataset was constructed by randomly drawing 25\,000 cases from the training dataset and noise was added to each simulation to mimic a new measurement set.

@@

\section{Results}
%
In this section, QRNN is used to predict the NFCS values for operational humidity channels. The main aim of this study is to demonstrate that sub-mm channels can be used to formulate the cloud filtering/correction of data measured around 183\,GHz. Different combinations of 183\,GHz channel and sub-mm channels are applied to QRNN and the results are compared. To determine the prediction performance of QRNN, the NFCS simulations are used as reference. Results from both pure-filtering and correction are described. Furthermore, the case specific uncertainties obtained from QRNN are also discussed.

\subsection{QRNN network structure}
%
A high performing QRNN model requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. We use quantile loss and CRPS for evaluation of the model performance.

For the structural parameters, usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. In this study, all possible hyper-parameters were not tested. We investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The others were chosen empirically.

@@

\subsection{ICI}
\subsubsection{Example results}
%
QRNN predictions are estimates of the posterior distribution over different quantiles. For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The quantiles are interpreted as probabilistic predictions and can be used to construct a probability distribution of the predictions. This is in sharp contrast to correction approaches which give out only point estimates. As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases. These results are from QRNN-single for channel I2V. The three cases shown in the figure have almost a similar median value but very different spread. The spread of the distributions can also be expressed as the prediction interval. If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval. It is gives the range where the prediction could be located and its length is a measure of the reliability. Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability. While the other two cases have longer intervals implying higher fluctuations, or low reliability.

@@

\subsubsection{Error of best estimate}
%
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure*}
%f 
\begin{figure*}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``Uncorrected'' represents the measurements and ``Filtered(5\,K)'' represents the dataset when no correction is made but cases with cloud correction greater than 5\,K are omitted. `Predicted'' denotes the entire prediction dataset, while ``Predicted(5\,K)'' refers to the predicted dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure*}

%t
\begin{table*}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V. Results from both QRNN-simple and QRNN-all are shown. The label ``Filtered'' refers to the dataset where cases with cloud correction greater than 5\,K are filtered out, and  no other correction is made. The label ``Predicted(All)'' refers to the complete predicted dataset, while in ``Predicted (5\,K)'', cases with cloud correction greater than 5\,K are removed from the predicted dataset. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:error_statistics_ici}
%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-single} & \multicolumn{3}{c}{QRNN-all}\\
		\cline{3-10}
%		\hline
		&&   Clear-sky &   All-sky &  Filtered & Predicted & Predicted &   Filtered & Predicted & Predicted \\
		&&&&							(5\,K) &(All)& (5\,K) & (5\,K)&(All)& (5\,K)\\
		\middlehline
%		\multicolumn{7}{c}{Channel - I1V}\\

Channel I1V& Bias     &  0.00 & -1.88 & -0.32(6.1\%) & -0.06 & -0.04 & -0.31(6.1\%) & -0.06 & -0.04 \\
			&MAE      &  0.64 &  2.32 &  0.79 &  0.64 &  0.55 &  0.78 &  0.61 &  0.54 \\
			&STD      &  0.80 &  8.84 &  1.07 &  0.98 &  0.73 &  1.07 &  0.91 &  0.71 \\
			&Skewness & -0.01 & -8.10 & -1.53 & -1.53 & -0.75 & -1.52 & -1.07 & -0.55 \\
\middlehline
Channel I2V &Bias     & -0.00 &  -1.04 & -0.24(3.7\%) & -0.01 & -0.00 & -0.24(3.6\%) & -0.05 & -0.03 \\
			&MAE      &  0.64 &   1.52 &  0.74 &  0.52 &  0.46 &  0.75 &  0.44 &  0.39 \\
			&STD      &  0.80 &   5.95 &  0.99 &  0.82 &  0.59 &  0.99 &  0.67 &  0.50 \\
			&Skewness &  0.00 & -10.80 & -1.10 & -2.17 & -0.27 & -1.05 & -2.22 & -0.27 \\
\middlehline	
Channel I3V &Bias     & -0.00 &  -0.63 & -0.18(2.3\%) &  0.01 &  0.02 & -0.19(2.2\%) & -0.03 & -0.03 \\
			&MAE      &  0.64 &   1.15 &  0.71 &  0.51 &  0.47 &  0.72 &  0.46 &  0.42 \\
			&STD      &  0.80 &   4.27 &  0.93 &  0.77 &  0.59 &  0.95 &  0.68 &  0.54 \\
			&skewness & -0.00 & -13.41 & -0.86 & -1.75 & -0.11 & -0.93 & -1.53 & -0.14 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

\begin{table*}[t]
	\caption{A comparison of the error statistics from QRNN-single and QRNN-all, when only cases with cloud correction greater than 10\,K are included. The fraction of cases forming the dataset are included in the parentheses}
	\label{tab:error_statistics_ici_high_cloud_impact}
	%	\tabcolsep=0.11cm
	\begin{tabular}{lrr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{I1V}& \multicolumn{2}{c|}{I2V} & \multicolumn{2}{c}{I3V}\\
		\cline{2-7}
		&QRNN-single& QRNN-all & QRNN-single & QRNN-all  & QRNN-single & QRNN-all\\
		\middlehline
				    Bias     & -0.53(4.02\%) & -0.38(4.07\%)  & -0.42(2.26\%) & -0.46(2.25\%) & -0.25(1.32\%) & -0.40(1.28\%) \\
					MAE      &  2.32 &  1.93  &  2.77 &  2.08 &  3.10 &  2.59 \\
					STD      &  3.13 &  2.63  &  3.65 &  2.85 &  4.03 &  3.47 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

\begin{figure}[t]
	\includegraphics[width=70mm]{Figures/different_filtering_thresholds.pdf} 
	\caption{A comparison of the  average error bias when pure-filtering approach (QRNN-single) is applied with different thresholds (red curves). The corresponding fraction of cases rejected is also shown on the right y-axis(blue curves).}
	\label{fig:filtering_thresholds}	
\end{figure} 
To assess the accuracy of QRNN predictions, a point estimate of the posterior distribution is required. Usually for Bayesian analysis, the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted clear-sky value.

The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig.~\ref{fig:PDF_predictions}. The distributions of corresponding NFCS simulations are also plotted as reference. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails. The degree of mismatch is highest for I1V, which incidently also has the largest spread of brightness temperatures in the clear-sky conditions. For all three channels, the colder brightness temperatures are under-estimated by QRNN, while a tendency to over-estimate the warmer brightness temperatures is seen for I1V and I2V.

For a quantitative evaluation of QRNN accuracy, the prediction errors are calculated as the deviation of the best estimate to its corresponding NFCS values. We calculate the mean bias, MAE (mean absolute error) and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. Fisher-Pearson coefficient of skewness is used to calculate the measure of skewness: 
\begin{equation}
g_1 = \frac{m_3}{m_2^{3/2}}, 
\end{equation}
where $m_2$ and $m_3$ are biased sample's second and third central moments.

Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels from QRNN-single. The distribution of noise is also plotted for reference. Without any cloud impact, the error distributions should follow a Gaussian distribution, and the skewness should be close to zero. However the presence of clouds leads to a brightness temperature reduction, and introduces a high negative bias among the deviations. Among the three channels, I1V has the highest cloud impact, while I3V has the least. After correction of the cloud impact, the resulting error distributions are  symmetric with a sharper peak albeit with a large spread. The large spread is due to cases which end up with partial cloud correction and also due to cases where the predicted values are warmer than the simulations. For all three channels quite similar behaviour is observed, though I1V has the highest number of cases with residual cloud impact. We assume that such cases are associated with high cloud impact. To validate our assumption, we implemented a pure-filtering approach. In the filtered subset, we removed all cases with QRNN cloud correction greater than 5\,K, and did not correct the remaining cases. This can be considered as a pure-filtering approach. The results from this subset are also displayed in the figure (red curve). For all three channels, the right side follows measurement noise, as expected, but the left side has substantial cases with small cloud impact which pass through the filter. However, since the spread of filtered dataset is smaller than the corrected one, it confirms our assumption that most of the partially corrected cases have high cloud impact. On the other hand, if all the predicted cases with correction less than 5\,K (Predicted (5\,K) in the figure) are considered, the resulting error distributions are quite close to the measurement noise, except for I1V, where few cases with residual cloud impact can still be seen.

@@

Similar results are seen for channel I2V, though a better performance of QRNN is observed. In I2V, the measurement bias is -1.04\,K which reduces to -0.01\,K after correction. The MAE also reduces from 1.52\,K to 0.52\,K. Removing cases with correction greater than 5\,K from the corrected dataset removes only 3.7\% of the data but reduces the absolute error to 0.46\,K and the bias to 0\,K. The standard deviation of the resulting dataset is only 0.59\,K as compared to 0.80\,K from noise. The reduction in the variability is also evident in the Fig~\ref{fig:error_distributions}, where the peak of the predicted distributions is sharper.

In comparison to I1V and I2V, I3V has the lowest fraction of the measurements with significant cloud impact. The bias in the measurements is only -0.63\,K in comparison to -1.88 in I1V. Pure-filtering removes 2.3\% of the total cases as cloudy, reduces the bias to 0.18\,K, and the standard deviation to 0.91\,K but nonetheless, cannot provide a complete cloud filtering. After correction of all the cases in the test dataset, the bias reduces to 0.01\,K and the MAE to 0.51\,K from 1.15\,K. Including correction along with filtering reduces the bias further down to 0.02\,K and standard deviation to 0.59\,K, which is again smaller than that of noise(0.80\,K).
